Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-25 mu/article/article.tex
Description for V^x and v^y completed for Alt structure.

values near to 30\,Km/s for the first zone mentioned before and 20\,Km/s for

@@

@@

same intensity giving a total spin-velocity near to 30\,Km/s and spin angles
$\theta$ and $\varphi$ near to $45.8^{\circ}$ and $40.7^{\circ}$, respectively.

@@

resulting in a spin-velocity magnitude near to 20\,Km/s. In this case the spin
angle over the $xy$ plane have values near to $290^{\circ}$ and the
corresponding polar angle correspond to values near to $153^{\circ}$.

@@

@@

Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$, we notice that this
response is almost two times more intense than $|\mathcal{V}^{\mathrm{x}}|$. For
the energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more
intense response than $yx$ and $yy$ components. This results in a spin azimuthal
angle near to $221^{\circ}$ and polar angle near to $141^{\circ}$.

@@

For the energy range all three components have
almost the same intensity resulting in a spin-velocity near to 50\,Km/s in both
cases.

@@

negative for the energy range from 0.65\,eV to 0.95\,eV \textcolor{red}{keeping

>>>>

values of 30\,Km/s for the first zone mentioned before and 20\,Km/s for

@@

% %% files: vab-rtp.sm_0.03_x_14452_65-spin_scissor_0_Nc_32_ang_145
% %%        alt-plots/alt-vab-rtp.gp

@@

same intensity giving a total spin-velocity of 19.3\,Km/s and spin polar and azimuthal angles
$\varphi = 45.8^{\circ}$ and $\theta=40.7^{\circ}$.

@@

resulting in a spin-velocity magnitude of 30.9\,Km/s being this magnitude the
most intense for $|\mathcal{V}^{\mathrm{x}}|$. In this case the polar angle is
$\varphi=153.8^{\circ}$ and the spin angle over the $xy$ plane have is $\theta=290.4^{\circ}$.

@@

% %% files: vab-rtp.sm_0.03_y_14452_65-spin_scissor_0_Nc_32_ang_145
% %%        alt-plots/alt-vab-rtp.gp

@@

Making now the analysis for $|\mathcal{V}^{\mathrm{y}}|$ we have that for the
energy range from 0.70\,eV to 0.74\,eV the $yz$ component have a more intense
response than $yx$ and $yy$ components and they give a total spin-velocity of
51.9\,Km/s and result in polar angle $\varphi=140.7^{\circ}$ and spin azimuthal
angle of $\theta=221.5^{\circ}$.

@@

For the energy range from 0.88\,eV to 0.95\,eV all three components have similar
intensities resulting in a spin-velocity magnitude of
$|\mathcal{V}^{\mathrm{y}}| =$ 52.3\,Km/s being this response 1.7 times mores
intense than the most intense response of $|\mathcal{V}^{\mathrm{x}}|$. The
corresponding polar and azimuthal angles for $|\mathcal{V}^{\mathrm{y}}|$ in
this energy range are $\theta = 129.0 ^{\circ}$ and $\varphi = 228.9 ^{\circ}$.

@@

negative for the energy range from 0.60\,eV to 1.0\,eV \textcolor{red}{keeping
